Probability

### 2016-04-28 prob.tex
import Amr's question from email to prepare a respond with formulas...

>>>>

\amr{Look at the first few pages of \cite{JamisonLodwick2004}. This
is consistent with some of the other things I have read. The way you
assign probability in this imprecise world is something like this:

- define some intervals

- the probability of an event is in $[x,y]$ where $x$ is some kind
of necessity and $y$ is some of belief.

So $[\frac{1}{2},1]$ would mean that the event must at least have
probability $\frac{1}{2}$ but I have reasons to believe it might
be certain. What is important I think is that two such events when
combined would combine to $[1,1]$ because the belief gets adjusted
based on the actual probabilities.

So perhaps we just need to adjust the intervals we choose for L5 and
change the $\vee$ operation to reflect this understanding and it
would be more intuitive?

\textemdash Amr

> On Apr 28, 2016, at 12:35 AM, Sabry, Amr A. <sabry@indiana.edu>
wrote:

>

> A quick thought. I don\textquoteright t like that the probability
of the entire space is $\likely$ and I don\textquoteright t like
the $\overflow$. I am absolutely sure other people have worked out
similar examples in possibility theory, dempster-shafer, Look at \textquotedblleft See
Also\textquotedblright{} near the end of \textquotedbl{}https://en.wikipedia.org/wiki/Dempster\textendash Shafer\_theory\textquotedblright .
I think there must be a way a simpler way of choosing the subsets
(intervals) to make things more intuitive. \textemdash Amr

> }
